### 2018-06-11 VV570/HW3/assignment.tex
all fulfilled

		\item 
			Althouth $C$ is uncountable, but the measure of its complement is 1, which is illustrated below, thus the measure of $C$ is 0.		
			\begin{equation}
				\begin{aligned}
					\lambda(C^c) & = \frac{1}{3} + 2 * \frac{1}{9} + ... \\
					             & = \frac{1}{3}\sum_{i=0}^{\infty} (\frac{2}{3})^n\\
					             & = \frac{1}{3} \lim\limits_{n\rightarrow\infty}\frac{1-(2/3)^n}{1-(2/3)}\\
					             & = 1
          		\end{aligned}
			\end{equation}

@@

				and the target $N$ is given as above.
			\end{proof}
		\item 
			\begin{proof}
				As $f_c(x)$ is continous over $[0, 1]$, it is left to prove that a continous function on a compact is uniformly continous, which can be proved by contradiction.

@@

		\item

@@

%----------------------------------------------------------------------------------------
%	PROBLEM 3
%----------------------------------------------------------------------------------------
\section{Taylor's theorem}
	\begin{enumerate}
		\item

		\item

@@

				\begin{equation}
					e = \frac{p}{q} 
				\end{equation}
				Thus
				\begin{equation}
					p(q-1)! = q! \sum_{i=0}^{q} \frac{1}{i!} +  q! \sum_{i=q+1}^{\infty} \frac{1}{i!} 
				\end{equation}
				Since both LHS  and  the first part of RHS are integers, the second part of RHS(denoted as $RHS_2$) should be an integer as well.//
				$RHS_2$ can be further expanded as below
				\begin{equation}
					\begin{aligned}
						RHS_2 & = \frac{1}{q+1} + \frac{1}{(q+1)(q+2)} + \frac{1}{(q+1)(q+2)(q+3)} + ...\\
						           & <  \frac{1}{q+1} + \frac{1}{(q+1)^2} + \frac{1}{(q+1)^3} + ...\\
						           & = \frac{1}{q}\\
						           & < 1
					\end{aligned}
				\end{equation}
				Therefore $RHS_2$ is not an integer as $RHS_2 > 0$. Thus the assumption fails, and $e$  is irrational.
			\end{proof}

>>>>

		\item 
			Althouth $C$ is uncountable, but the measure of its complement is 1, which is illustrated below, thus the measure of $C$ is 0.		
			\begin{equation}
				\begin{aligned}
					\lambda(C^c) & = \frac{1}{3} + 2 * \frac{1}{9} + ... \\
					             & = \frac{1}{3}\sum_{i=0}^{\infty} (\frac{2}{3})^n\\
					             & = \frac{1}{3} \lim\limits_{n\rightarrow\infty}\frac{1-(2/3)^n}{1-(2/3)} = 1
          		\end{aligned}
			\end{equation}

@@

				and the target $N$ is given as above.
			\end{proof}
		\item 
			\begin{enumerate}
				\item 
					\begin{proof}
						As $f_c(x)$ is continous over $[0, 1]$, it is left to prove that a continous function on a compact is uniformly continous, which can be proved by contradiction.\\
						(the proof haven't figured out yet...)
					\end{proof}

				\item 
					\begin{proof}
						For any $x \in (0, 1] \cap C$, $f_c(x)$ can be expressed as below

						\begin{equation}
							f_c(x) = sup\{ f_c(y) | y < x, y \in [0, 1] \backslash C  \}
						\end{equation}

						Thus $f_c(x)$ is monotonically increasing.
					\end{proof}

				\item
					\begin{proof}
						As $f_c(x)$ is constant on each segment dropped by $C$, thus $f_c'(x)$ is almost 0 everywhere.
					\end{proof}

		\item 
			\begin{proof}
				Assume $f_c(x)$  is absolutely continous, then its Riemann integral exists, which can be expressed as 
				\begin{equation}
					\int_{0}^{1} f_c'(x) dx = f_c(1) - f_c(0) \label{cantor_rie}
				\end{equation}

				However, the $LHS$ of (\ref{cantor_rie}) is 0 as $f_c'(x)$ is 0 almost everywhere, while the $RHS$ of (\ref{cantor_rie}) is 1. Thus its riemann integral doesn't exist, and therefore the assumption fails.

@@

@@

%----------------------------------------------------------------------------------------
%	PROBLEM 3
%----------------------------------------------------------------------------------------
\section{Taylor's theorem}
	\begin{enumerate}
		\item 
			\begin{proof}
				For $n=0$, apply the fundamental theorem of calculus to $f(x)$ and its derivatives, $f(x)$ can be written as below. It's clear that the theorem is valid in such case.
				\begin{equation}
					f(x) = f(a) + \int_{a}^{x} f'(t) dt
				\end{equation}

				Suppose the theorem is still valid for $n = k$, then $f(x)$ can be written as 
				\begin{equation}
					f(x) = \sum_{i=0}^{k}\frac{f^{i}(a)}{i!}(x-a)^i + \frac{1}{k!}\int_{a}^{x} (x-t)^k f^{(k+1)}(t) dt \label{rhs}
				\end{equation}

				For $n = k+1$, as $f^{(k+1)}$ is absolutely continous, apply the fundamental theorem of calculus to $f^{(k+1)}$, the second part of RHS of $f(x)$ can be written as below
				\begin{equation}
					\begin{aligned}
						RHS_2 & = \frac{1}{k!}\int_{a}^{x} (x-t)^k [f^{(k+1)}(a) + \int_{a}^{t}f^{(k+2)}(u) du] dt\\
						           & = \frac{f^{(k+1)}(a)}{k!}\int_{a}^{x}(x-t)^k dt + \frac{1}{k!}\int_{a}^{x}(x-t)^k \int_{a}^{t} f^{(k+2)}(u) du dt\\
						           & =  \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} + \frac{1}{k!}\int_{a}^{x}(x-t)^k \int_{a}^{t} f^{(k+2)}(u) du dt
					\end{aligned}
				\end{equation}
				Let
				\begin{equation}
					g(t) = \int_{a}^{t} f^{(k+2)}(u) du
				\end{equation}
				$RHS_2$ can be further expressed as
				\begin{equation}
					\begin{aligned}
						RHS_2 & =  \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} + \frac{1}{k!}\int_{a}^{x}(x-t)^k g(t) dt\\
								   & =  \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} - \frac{1}{(k+1)!}\int_{a}^{x} g(t) d(x-t)^{k+1}\\
								   & =  \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} - \frac{1}{(k+1)!}[\left. (x-t)^{k+1} g(t) \right|_{a}^{x} - \int_{a}^{x}(x-t)^{k+1} g'(t) dt]
					\end{aligned}
				\end{equation}
				As $g(a) = 0$ and $g'(t) = f^{(k+2)}(t)$, $RHS_2$ can be simplified as 
				\begin{equation}
					RHS_2 = \frac{f^{k+1}(a)}{(k+1)!}(x-a)^{k+1} + \frac{1}{(k+1)!}\int_{a}^{x}(x-t)^{k+1}  f^{(k+2)}(t)dt \label{rhs2}
				\end{equation}

				Substitude (\ref{rhs2}) into (\ref{rhs}), $f(x)$ can be expressed as below when $n = k+1$
				\begin{equation}
					\begin{aligned}
						f(x) & = \sum_{i=0}^{k+1}\frac{f^{i}(a)}{i!}(x-a)^i + \frac{1}{(k+1)!}\int_{a}^{x} (x-t)^{k+1} f^{(k+2)}(t) dt\\
						      & = \sum_{i=0}^{n}\frac{f^{i}(a)}{i!}(x-a)^i + \frac{1}{n!}\int_{a}^{x} (x-t)^{n} f^{(n+1)}(t) dt\\
					\end{aligned}
				\end{equation}
				Thus the theorem is still valid when $n$ is extended to $k+1$.
			\end{proof}

		\item 
			\begin{proof}
				It is left to prove that there exists $c\in [a, x]$ s.t. 
				\begin{equation}
					\frac{1}{n!}\int_{a}^{x} (x-t)^{n} f^{(n+1)}(t) dt = \frac{f^{(n+1)}(c)}{(n+1)!}(x-a)^{n+1}
				\end{equation}
				which is equal to 
				\begin{equation}
					(n+1)\int_{a}^{x} (x-t)^{n} f^{(n+1)}(t) dt = f^{(n+1)}(c)(x-a)^{n+1} \label{target}
				\end{equation}

				As the LHS of (\ref{target}) can be expanded as below
				\begin{equation}
					\begin{aligned}
						LHS & = - \int_{a}^{x}f^{(n+1)}(t) d(x-t)^{n+1}\\
							   & = - [\left. (x-t)^{n+1}f^{(n+1)}(t)\right|_{a}^{x} - \int_{a}^{x}(x-t)^{n+1}df^{(n+1)}(t)]
					\end{aligned}
				\end{equation}

				Apply the medium value theorem ...(haven't figured out yet...)

@@

				\begin{equation}
					e = \frac{p}{q} 
				\end{equation}
				Thus
				\begin{equation}
					p(q-1)! = q! \sum_{i=0}^{q} \frac{1}{i!} +  q! \sum_{i=q+1}^{\infty} \frac{1}{i!} 
				\end{equation}
				Since both LHS  and  the first part of RHS are integers, the second part of RHS(denoted as $RHS_2$) should be an integer as well.//
				$RHS_2$ can be further expanded as below
				\begin{equation}
					\begin{aligned}
						RHS_2 & = \frac{1}{q+1} + \frac{1}{(q+1)(q+2)} + \frac{1}{(q+1)(q+2)(q+3)} + ...\\
						           & <  \frac{1}{q+1} + \frac{1}{(q+1)^2} + \frac{1}{(q+1)^3} + ...\\
						           & = \frac{1}{q} < 1 \\
					\end{aligned}
				\end{equation}
				Therefore $RHS_2$ is not an integer as $RHS_2 > 0$. Thus the assumption fails, and $e$  is irrational.
			\end{proof}
